Airspace configuration decision based on Monte-Carlo tree search

### 2018-04-13 article/article.tex
(+) added mcts algo (not definitive)
(~) a bit more precise on the state of the art

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}

@@

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
~\cite{bedouet2016} determined workload density proportionally to the time
spent by aircraft in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircraft. On the other hand, more complex method,
involving many more inputs are also available, such as a neural network
forecasting the workload~\cite{gianazza2010forecasting}. This is the method we
are going to use in this paper.

@@

>>>>

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}

@@

In most cases the cost of a configuration is based on the workload. Each
approach seems to give their own representation of the workload. For instance,
~\cite{bedouet2016} determined workload density proportionally to the time
spent by aircraft in each sector. A simpler version~\cite{sergeeva2017dynamic}
only uses the number of aircraft. On the other hand, more complex methods,
involving many more inputs are also available. For instance
,~\cite{gianazza2010forecasting} used several indicators, such as sector
volume, or vertical incoming flows in the next 15 and 60 minutes. Those
indicators ease the training of a neural network forecasting the workload.

@@

\section{Model}

\section{Algorithm}
\subsection{Monte Carlo tree search overview}
\begin{algorithm}
  \caption{General MCTS~\cite{browne2012survey}}
  \begin{algorithmic}
    \Procedure{MctsSearch}{$v_0$}
    \While{within computational budget}
    \State{} \(v_l \gets\) \Call{TreePolicy}{$v_0$}
    \State{} \(\Delta \gets\) \Call{DefaultPolicy}{$s(v_l)$}
    \State{} \Call{Backup}{$v_l$, $\Delta$}
    \EndWhile{}
    \Return{\(a(\)\Call{BestChild}{$v_0$}\()\)}
    \EndProcedure{}
  \end{algorithmic}

\end{algorithm}
